---
output:
  html_document:
    number_sections: yes
    theme: spacelab
    toc: yes
    toc_depth: 3
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '3'
geometry: margin=1in
---
title: "Analisis Oeste 25 GH Trigo"

```{r, echo=FALSE,results='hide'}
#source('~/Box Sync/R_libraries_load/library.R')
library(tmap)
library(rgdal)
library(Grid2Polygons)
library(plm)
library(stargazer)
library(tidyverse)
library(data.table)
library(sf)
#opts_chunk$set(
 # comment = NA,
  #message = FALSE,
  #warning = FALSE,
  #echo=FALSE,
  #tidy=FALSE,
  #size='footnotesize'
  #)
#opts_knit$set(root.dir='~/Box Sync/ResearchProjects/DIFM')
setwd("C:/Users/lapuntel/Dropbox/Clarion/Ensayos DIFM/Ensayos_2017_Trigo/Grobocopatel/Oeste_Laila")
```

```{r,cache=TRUE}
#===================================
# Preparation
#===================================
#--- import the data ---#
#data <- fread('./Data/Oeste_Laila_17/Oeste25.csv') %>% 
#	setnames(names(.),tolower(names(.)))

data <- fread('./Oeste25.csv') %>% 
	setnames(names(.),tolower(names(.)))

```

# Visualization of the data

```{r, cache=TRUE}
ggplot(data=data) +
	geom_point(aes(y=lat,x=long,color=yld_mass_d))
```

# Regression

```{r, cache=TRUE}

library(mgcv)
gam_res <- gam(yld_mass_d ~
	s(rate,k=5)+
	s(ec90,k=5)+
	I(rate*ec90)+
	s(long,k=10)+
	s(lat,k=10)+
	ti(long,lat,k=10),
	data=data) 
summary(gam_res)
plot(gam_res)
```

# Visualization of the results

```{r}
#--- list of N rate values ---#
rate_ls <- seq(min(data$rate),max(data$rate),length=1000)

#--- list of values of EC we consider ---#
ec_ls <- quantile(data[,ec90],prob=c(0.05,0.5,0.95))
```

```{r }
#--- new data for prediction ---#
data_new <- expand.grid(rate_ls,ec_ls) %>% 
	data.table() %>% 
	setnames(names(.),c('rate','ec90')) %>% 
	.[,long:=data[,mean(long)]] %>% 
	.[,lat:=data[,mean(lat)]]  

#--- yhat and se ---#
yhat <- predict(gam_res,newdata=data_new,se.fit=TRUE)
```

```{r }
#--- Calculate profit and se ---#
data_plot <- data_new %>%  
	.[,y_hat:=yhat$fit] %>% 
	.[,y_hat_se:=yhat$se.fit]  
```

## Yield response to nitrogen rate for various levels of EC (deep) 

```{r, cache=TRUE}
ggplot() +
	geom_line(data=data_plot,aes(y=y_hat,x=rate,color=factor(ec90)))

```

# Profit maximizing nitrogen rate

```{r, cache=TRUE}
Pn <- 0.35 # $/kg
Pw <- 160 # $/ton
rate_ls <- seq(0,400,length=1000)
ec_ls <- seq(min(data$ec90),max(data$ec90),length=100)
pi_data <- expand.grid(rate_ls,ec_ls) %>% 
	data.table() %>% 
	setnames(names(.),c('rate','ec90')) %>% 
	.[,long:=data[,mean(long)]] %>% 
	.[,lat:=data[,mean(lat)]] %>% 
	.[,yhat:=predict(gam_res,newdata=.)] %>% 
	.[,pi_hat:=Pw*yhat-Pn*rate] %>% 
	.[,.SD[which.max(pi_hat),],by=ec90]  

gam_opt_N <- gam(rate ~ s(ec90,k=4),data=pi_data)
# plot(gam_opt_N)
```

```{r, cache=TRUE}
ggplot(data=pi_data) +	
	geom_line(aes(y=rate,x=ec90)) +
	xlab('EC 90 (ds/m)') +
	ylab('Dosis Optima de Urea (kg/ha)') +
	ggtitle('El Impacto de la EC90 en la dosis optima de urea')
```

```{r, cache=TRUE}
mean_long <- data[,mean(long)]
mean_lat <- data[,mean(lat)]

#veris <- st_read(dsn='~/Box Sync/ResearchProjects/DIFM/Data/Oeste_Laila_17/Laila_Oeste_additional','Veris') %>% 
veris<- st_read(dsn= "Additional/Veris.shp" ) %>%
	setnames(names(.),tolower(names(.))) %>% 
	filter(ec90<max(data$ec90))

farmer_pi <- veris %>% 
	mutate(
		rate=180,
		long=mean_long,
		lat=mean_lat
		) %>% 
	mutate(
		yhat_f=predict(gam_res,newdata=.),
		pi_hat_f=Pw*yhat_f-Pn*rate
		)

opt_pi <- veris %>% 
	mutate(
		rate=predict(gam_opt_N,newdata=.),
		long=mean_long,
		lat=mean_lat
		) %>% 
	mutate(
		yhat_o=predict(gam_res,newdata=.),
		pi_hat_o=Pw*yhat_o-Pn*rate
		)

all_pi <- cbind(farmer_pi,opt_pi) %>% 
	mutate(pi_dif=pi_hat_o-pi_hat_f)  
mean(all_pi$pi_dif)
min(all_pi$pi_dif)
max(all_pi$pi_dif)

  all_pi %>%
  ggplot( aes(x=pi_dif) )+ #, fill=region)
  geom_density() #+xlim(0,100)
```

## Profit differentials between farmer-chosen and recommended rates by EC

Loss mostly come from not applying enough nitrogen at parts of the field with high EC.

```{r, cache=TRUE}
ggplot(data=all_pi) +
	geom_line(aes(y=pi_dif,x=ec90)) +
	xlab('EC 90') +
	ylab('Diferencia en margen ($/ha)') +
	ggtitle('Diferencia en margen entre dosis fija y optima en diferente EC 90')

ggplot(data=all_pi) +
	geom_histogram(aes(x=ec90),fill='white',color='blue') +
	xlab('EC 90') +
	ggtitle('Distribucion de EC (90)')
```

# Optimal seed rate map

## Optimal variable rate map

```{r opt_map, cache=TRUE,fig.width=6,fig.height=6}
ec_poly <- readGDAL('./Oe_25_ECclip1.tif') %>% 
	as(.,'SpatialPolygonsDataFrame') %>% 
	st_as_sf() %>% 
	setnames('band1','ec90') %>% 
	mutate(opt_N=predict(gam_opt_N,newdata=.)) %>% 
	filter(ec90<max(data$ec90))
```

```{r, cache=TRUE,dependson='opt_map'}
tm_shape(ec_poly) +
	tm_fill('opt_N') +
	tm_layout(
        legend.outside=TRUE
        )	
# how their application fairs against the optimal one
# optimal uniform rate 
```

## Optimal uniform Urea rate

```{r, cache=TRUE}
n_ls <- 230:280
data_pi <- ec_poly %>% 
	data.table() %>% 
	.[rep(1:nrow(ec_poly),each=length(n_ls)),] %>% 
	.[,rate:=rep(n_ls,nrow(ec_poly))] %>% 
	.[,long:=data[,mean(long)]] %>% 
	.[,lat:=data[,mean(lat)]] %>% 
	.[,yhat:=predict(gam_res,newdata=.)] %>% 
	.[,pi_hat:=Pw*yhat-Pn*rate] 

opt_N_unif <- data_pi[,.(pi_hat=mean(pi_hat)),by=rate] %>% 
	.[,.SD[which.max(pi_hat),]]

opt_N_unif$rate
```

## Optimal uniform vs variable?

```{r, cache=TRUE}
all_pi %<>%  data.table(.) %>% 
	.[,rate:=opt_N_unif$rate] %>% 
	.[,yhat_opt_u:=predict(gam_res,newdata=.)] %>% 
	.[,pi_opt_u:=Pw*yhat_opt_u-Pn*rate]  
```

The average difference in profitability between the variable and uniform rates is:

```{r, cache=TRUE}
#all_pi %$% mean(pi_hat_o-pi_opt_u)
```


